%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
\cventry
	{Freelance: Technical Consultant}  % Job title
    {Penske Logistics} % Organization
    {Roosendaal, The Netherlands} % Location
    {04/2018 - Current} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
       \item {Provisioned an easily manageable European infrastructure, working towards IaC (Infrastructure as Code) with tools like Ansible.}
       \item {Removed old network and networking equipment.}
       \item {Build the new DMZ on independent RIPE LIR membership for flexibility in the future having own IPv4 and IPv6 space.}
       \item {Migrated DNS and DHCP into the Enterprise DDI which is Infoblox.}
       \end{cvitems}
	}
%---------------------------------------------------------
  \cventry
    {Founder \& CEO} % Job title
    {PureXperts} % Organization
    {Rijen, The Netherlands} % Location
    {01/2013 - 12/2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {System \& Networking Consultancy firm providing highly technical solutions for 5 years, due to the inability to return to Holland (covid19) the company has been stopped by Governmental orders.}
        \item {Built and deployed overall service infrastructure utilizing Docker container, focusing on high-availability, fault tolerance, and auto-scaling.}
        \item {Developed an easy-to-use Network Automation while utilizing python which simplified the job for the customers and reduced operational budgets.}
	\item {Provide skilled consultants to our clients from our own payroll or 3rd party}
	\item {Maintained project(s) (deadlines) while having good understanding of service management frameworks.}
      \end{cvitems}
}
%---------------------------------------------------------
 \cventry
    {Contractor: Technical Consultant} % Job title
    {Deutsche Glasfaser} % Organization
    {Borken, Germany} % Location
    {08/2018 - 08/2019} % Date(s)
{
      \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Testing software for edge platform (BNG routers \& Edge switches).}
      \item {Implementing software lifecycle management.}
      \item {CGN (2020) for 1000Gbps.}
      \item {Network 2020 strategy and product selection.} 
      \item {Supervision of Cisco TAC cases.}
      \end{cvitems}
}
%---------------------------------------------------------
 \cventry
    {Contractor: Technical Consultant} % Job title
    {CAIW Diensten} % Organization
    {Naaldwijk, The Netherlands} % Location
    {12/2017 - 03/2018} % Date(s)
	{
      \begin{cvitems} % Description(s) of tasks/responsibilities
    \item {Create High Level Design template.}
    \item {Research future growth by using GPON.}
    \item {Development of an IPTV solution that can be managed from the Cloud and has a limited internet set available for greater security.}
    \item {Supervision Cisco TAC cases.}
      \end{cvitems}
}

%---------------------------------------------------------
  \cventry
	{Contractor: Lead Network Engineer} % Job title
	{Digital Media Center} % Organization
	{Amsterdam, The Netherlands} % Location
	{07/2017 - 11/2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
         \item {Develop a technical migration strategy for the replacement of the multicast network.}
   	 \item {Puppet in combination with GIT for automating work.}
	 \item {Perform migration \& project activities.}
  	 \item {3rd line support in the daily operation.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
	{Contractor: Sr. Network Engineer} % Job title
	{VION} % Organization
	{Boxtel, The Netherlands} % Location
	{04/2017 - 06/2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
          \item {Developing a technical migration strategy.}
	  \item {Perform migration \& project activities.}	
	  \item {3rd line support in the daily operation.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
        {Contractor: Network Engineer} % Job title
 	{Tele2} % Organization
 	{Diemen, The Netherlands} % Location
  	{02/2016 - 02/2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
          \item {Technical Migration Strategy (RFC).}
    \item {Perform migration \& project activities.}
    \item {3rd line support in the daily operation.}
    \item {Translation of business demands to infrastructure solutions.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Contractor: CCHS Network Architect} % Job title
    {Conclusion} % Organization
    {Utrecht, The Netherlands} % Location
    {05/2015 - 11/2015} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
          \item {Designing Low (Detail Network Design) \& High Level Designs (Generic Detail Network Design).}
    \item {Determine migration strategy (Playbook).}
    \item {2nd \& 3rd line support in carrying out daily activities.} 
    \item {Translation of business demands to infrastructure solutions.}
      \end{cvitems}
    }
%---------------------------------------------------------
 \cventry
    {Contractor: Network Specialist} % Job title
    {Fokker Elmo} % Organization
    {Utrecht, Netherlands} % Location
    {05/2015 - 11/2015} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
          \item {Designing Low (Detail Network Design) \& High Level Designs (Generic Detail Network Design). for .1x migration.}
    \item {Determine migration strategy (Playbook).}
    \item {Daily network support activities.}
      \end{cvitems}
    }
%---------------------------------------------------------
  \cventry
    {Contractor: Sr. Network Specialist} % Job title
    {ProRail} % Organization
    {Utrecht, The Netherlands} % Location
    {01/2014 - 12/2014} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Designing Low (Detail Network Design) \& High Level Designs (Generic Detail Network Design).}
        \item {Determine migration strategy (Playbook).}
	\item {3rd line support in carrying out the Migration (carrying out the steps in the Roadmap).}
	\item {QoS design.}
      \end{cvitems}
    }
%---------------------------------------------------------
  \cventry
    {Contractor: Network Consultant} % Job title
    {Peopleware} % Organization
    {Rotterdam, The Netherlands} % Location
    {01/2013 - 12/2015} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Support of a old Juniper SRX clusters and the new datacenter design.}
      \item {Operational support while the move was performed from the old to the new datacenter.}
      \end{cvitems}
    }
%---------------------------------------------------------
 \cventry
    {Contractor: Network Design Consultant} % Job title
    {Schiphol Telemetics} % Organization
    {Schiphol, The Netherlands} % Location
    {01/2014 - 06/2014} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Schiphol Group - replacement of routers for connection ST based on Cisco.}
      \item {Transavia - replacement switches for coupling ST based on Avaya.}
      \item {Capacity Management Document - Document serving guidelines for setting up Capacity Management.}
      \item {Next Generation Core Network design based on MPLS.}
      \end{cvitems}
    }
%---------------------------------------------------------
 \cventry
    {Contractor: WAN Specialist} % Job title
    {VGZ} % Organization
    {Apeldoorn, The Netherlands} % Location
    {09/2013 - 12/2013} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Helping with the development of the new WAN design.}
      \item {Supervising and implementing the realization of new WAN lines.}
	\item {Migrating existing WAN connections to the new connections on evenings and weekends}.
      \end{cvitems}
    }
%---------------------------------------------------------
 \cventry
    {Contractor: Technical RCA} % Job title
    {AT\&T} % Organization
    {Rijswijk, The Netherlands} % Location
    {11/2012 - 04/2013} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Describing technical RCAs or correcting RCAs with the right technical input.}
      \end{cvitems}
    }
%---------------------------------------------------------
\end{cventries}
